---
title: "A Tutorial to Matching"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "[Hongfei Li](https://hongfei-business.com/)"
date: "Last Updated: `r format(Sys.time(), '%B %d, %Y')`"
output: 
  rmarkdown::html_vignette:
    includes:

vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


This tutorial uses an empirical example to describe what we can achieve from MultiSeqCCoA. The package was written by [Ruoqing Zhu](https://sites.google.com/site/teazrq/). The reference of the paper that put forward this package is recommended as 

> "Cao X, Folta T, Li H, Zhu R (2019) A New Method to Understand the Online Word of Mouth Dynamics: Multi-View Sequential Canonical Covariance Analysis"

For all the authors' information, please see:
[Xian Cao](https://www.bsu.edu/academics/collegesanddepartments/management/about-us/faculty-and-staff/caoxian)
[Timothy Folta](https://www.business.uconn.edu/person/timothy-folta/)
[Hongfei Li](https://hongfeiuconn.github.io/personal-website/)
[Ruoqing Zhu](https://sites.google.com/site/teazrq/)

This paper is currently under review. For a detailed introduction to MultiSeqCCoA, please refer to <a href="MultiSeqCCoA.pptx#" class="download" title="MultiSeqCCoA.pptx">MultiSeqCCoA.pptx</a>.

## Import libraries

* All data filter and rearrangement are based on package [data.table](https://cran.r-project.org/web/packages/data.table/data.table.pdf).
* Anytime package is used for converting Unix time to real time.

```{r,  warning = FALSE}
library(MultiSeqCCA)
library(data.table)
library(anytime)
```

## Read Data




```{r,  warning = FALSE}
load("data.RData")
summary(data)

```







